\documentclass{letter}
\usepackage{hyperref}
\signature{Jonathan Starr}
\address{Jonathan Starr \\ 1205 Larkwood Drive \\ Austin, Texas 78723}
\begin{document}

\begin{letter}{}
\opening{Dear prospective employer:}

I am interested in the research associate engineering position with job reference identifier IIS-2017-31.
Working as a research associate at Fraunhofer is appealing because
    I
        enjoy the theory of algorithm development but 
        also want to see my work applied towards direct consumer applications.
Given your listed requirements and preferred qualifications for the applicant,
I believe that I am an excellent candidate and deserving of your consideration.

This position requires a background in
    digital signal processing and 
    the field of acoustics, and
as my r\'{e}sum\'{e} will show,
I have experience in these areas through my education and practical work experience.
I graduated with a master's degree in Digital Signal Processing (DSP) through the competitive Communications and Networking Systems department at the University of Texas.
As a graduate researcher,
I conducted novel research in the field of DSP and developed algorithms in Matlab and Python for applications in multi-user telecommunications networks.
Further, as a practicing engineer,
I worked as an acoustic analyst in the Advanced Technology Laboratory at Applied Research Laboratories (ARL).
Here I developed algorithms for sonar applications, and
I learned to appreciate the difficulties of operating in the extremely harsh acoustic propagation environment.
I left this role at ARL because I was interested in exploring a better work-life balance, but
I always found the problem area interesting and would be delighted to work in the field of acoustics again.

I would be pleased to further discuss my qualifications and to learn more about the position through an interview.
I live in the United States but will be able to accommodate any schedule during regular work hours in Germany.
Please contact me through my cellphone at +1.512.237.7562 or through my email \mbox{\href{mailto:jonstarr@utexas.edu}{jonstarr@utexas.edu}}.
Thank you for this opportunity and for your consideration.

\closing{Sincerely,}

\encl{r\'{e}sum\'{e}, list of references, and university transcript}

\end{letter}
\end{document}
